\textsf{Are large language models superhuman chemists?}

### 2024-10-30 src/tex/ms.tex
fix: update circle plots

\section*{Data and code availability}
The code and data for \chembench are available at \url{https://github.com/lamalab-org/chem-bench}.
The code for the app for our human baseline study is available at \url{https://github.com/lamalab-org/chem-bench-app}.
To ensure reproducibility, this manuscript was generated using the \href{https://show-your.work/en/latest/}{\showyourwork} framework.\autocite{Luger2021}
The code to rebuild the paper (including code for all figures and numbers next to which there is a GitHub icon) can be found at \url{\GitHubURL}.
To facilitate reproduction, some intermediate analysis results are cached at \url{http://dx.doi.org/10.5072/zenodo.34706}.

>>>>

\section*{Data and code availability}
The code and data for \chembench are available at \url{https://github.com/lamalab-org/chem-bench} and archived on Zenodo under \href{10.5281/zenodo.14010212}{https://zenodo.org/records/14010212}.
The code for the app for our human baseline study is available at \url{https://github.com/lamalab-org/chem-bench-app}.
To ensure reproducibility, this manuscript was generated using the \href{https://show-your.work/en/latest/}{\showyourwork} framework.\autocite{Luger2021}
The code to rebuild the paper (including code for all figures and numbers next to which there is a GitHub icon) can be found at \url{\GitHubURL}.
To facilitate reproduction, some intermediate analysis results are cached at \url{http://dx.doi.org/10.5072/zenodo.34706}.

### 2024-10-30 src/tex/sections/human_subset_selection.tex
Update src/tex/sections/human_subset_selection.tex
feat: cleanup text for submission (#62)

\paragraph{Question selection}

Several design choices were made when selecting a human subset. Firstly, from the full dataset, we keep all the questions that are labeled as advanced. In this way, we can obtain a deeper insight about the capabilities of \glspl{llm} on advanced tasks
when compared to actual chemists. Secondly, we sample a maximum of three questions across all possible combinations of categories (i.e., knowledge or reasoning) and topics (e.g., organic chemistry, physical chemistry). Thirdly, we do not include any intuition questions
in this subset, because the correct answers are subjective, and would hinder an objective evaluation of the chemists against \glspl{llm}. In total, \variable{output/num_human_answered_questions.txt} questions have been sampled for the human study. Then, this set is divided into two subsets based on the aforementioned combinations. One of the question subsets allows tool use, and the other does not.

>>>>

\paragraph{Question selection} \label{sec:subset-selection}

 Several design choices were made when selecting \chembenchmini. Firstly, from the full dataset, we kept all the questions labeled as advanced. In this way, we can obtain a deeper insight into the capabilities of \glspl{llm} on advanced tasks when compared to actual chemists. Secondly, we sample a maximum of three questions across all possible combinations of categories (i.e., knowledge or reasoning) and topics (e.g., organic chemistry, physical chemistry). Thirdly, we do not include any intuition questions in this subset because the intended use of \chembenchmini is to provide a fast and fair evaluation of \glspl{llm} independent of any human baseline. In total, \variable{output/num_human_answered_questions.txt} questions have been sampled for \chembenchmini. Then, this set is divided into two subsets based on the aforementioned combinations. One of the question subsets allows tool use, and the other does not.
